\%-----------EXPERIENCE-----------
        \section{Experience}
        \resumeSubHeadingListStart
    \resumeSubheading
              {Software Developer Intern}{Nov. 2020 -- Sep. 2021}{Miq Digital}{Bangalore, India}
              
    \resumeItemListStart
              
      \resumeItem {Contributed to the conversion of the application's UI to a new, optimized design, resulting in improved user experience.}
      \resumeItem {Overhauled legacy code to recent React code while adhering to best coding practices, resulting in increased maintainability.}
      \resumeItem {Implemented 3 forms, dependent on API calls, and stored their information and selections in Redux.}
      \resumeItem {Created a white-label version of the application for two external clients.}
      \resumeItem {developed  2  RESTful controllers for data manipulation, storage, and retrieval from AWS and internal services utilizing Spring MVC, Spring Boot, Spring JDBC}
      \resumeItem {Wrote 25-33 percent of front-end automated tests using Selenium and numerous back-end unit tests with Junit for quality assurance, reducing vulnerabilities, and enhancing deployment confidence..}
      \resumeItem {Detected and fixed bugs, user complaints, requests, permissions, and other issues across over 10 instances as the bug master and admin, supporting continuous integration and continuous delivery using Jenkins in agile scrum based enivroment .}
      \resumeItem {Co-authored two sets of documentation detailing the backend APIs of the applications and the onboarding process for new employees.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd\%-----------EDUCATION-----------
        \section{Education}
        \resumeSubHeadingListStart
    \resumeSubheading
              {Bachelor of Technology}{Vellore Institute of Technology, Vellore, India}{Computer Science and Engineering}{2018 - 2022}
  \resumeSubHeadingListEnd\%-----------PROJECTS-----------
        \section{Projects}
        \resumeSubHeadingListStart
    \resumeProjectHeading
            {\textbf{Blogging Website} $|$ \emph{TypeScript, React, Serverless, Tailwind, ORM}}
              {April 2024 - May 2024} 
    \resumeItemListStart
      \resumeItem {Built a dynamic and responsive front-end using React, Recoil, and Tailwind CSS.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd